\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-02-02 paper.tex
?
key sentences

\title{\LARGE \bf
Informed sampling for kinodynamic planning by \\ Markov Chain Monte Carlo methods
}

\author{
Rohan Thakker$^{*}$,
Cole Gulino$^{*}$,
Daqing YI$^{}$,
Oren Salzman$^{}$ and
Siddhartha Srinivasa$^{}$% <-this % stops a space
\thanks{*R. Thakker and C. Gulino contributed equally to this paper.}
\thanks{This work was (partially) funded by the National Science Foundation IIS (\#1409003), Toyota Motor Engineering \& Manufacturing (TEMA), and the Office of Naval Research.}% <-this % stops a space
\thanks{$^{1}${\tt\small \{rthakker, cgulino, daqingy, osalzman, ss5\} @andrew.cmu.edu}}%
%
\\        
Robotics Institute, Carnegie Mellon University$^{1}$
}

@@

%While, original sampling-based algorithms such as RRT~\cite{LK01} and PRM~\cite{KSLO96} only guaranteed to asymptotically return \emph{a} solution, if one exists, they did not provide any guarantees on the \emph{quality} of the solution, given some optimization criteria.
%Karaman and Frazzoli~\cite{KF11}, presented variants of PRM and RRT, named PRM* and RRT*, respectively that were shown to produce paths who's cost converges asymptotically to the minimal-cost path.
%Additional algorithms followed, increasing the converges rate by various techniques such as lazy dynamic programming~\cite{GSB15, JSCP15}, relaxing optimality to near-optimality~\cite{DB14, SH16} and more.
%

%In the most basic form, the motion-planning problem calls for computing \emph{a} path between two given states.
%Indeed, 
%However, recent years 
%Original planners such as RRT~\cite{LK01} and PRM~\cite{KSLO96} did not provide any guarantee on the \emph{s}

@@

\section{Motivating example---Minimal-Time Double Integrator}
We start by considering a simple yet important motion-planning problem---the double integrator.
We are given a one-dimensional point robot  with bounded velocity and bounded acceleration moving amid obstacles. We wish to compute the minimal-time trajectory between two states $x_s, x_g$.
A state in this model is described by 
the position $q \in \R$
and
the velocity $\dot{q}\in \R$ of the position
%each coordinate axis.
The dynamics of the system is described by:
$$
x = (q, \dot{q}); 
\hspace{5mm}
u = \ddot{q}.
$$
Here, the control $u \in [u_{\text{min}}, u_{\text{max}}]$ is the (bounded) acceleration.

>>>>

\title{\LARGE \bf
Informed sampling by Markov Chain Monte Carlo methods
}

\author{
Rohan Thakker$^{*}$,
Cole Gulino$^{*}$,
Daqing Yi$^{}$,
Oren Salzman$^{}$ and
Siddhartha Srinivasa$^{}$% <-this % stops a space
\thanks{*R. Thakker and C. Gulino contributed equally to this paper.}
\thanks{This work was (partially) funded by the National Science Foundation IIS (\#1409003), Toyota Motor Engineering \& Manufacturing (TEMA), and the Office of Naval Research.}% <-this % stops a space
\thanks{$^{1}${\tt\small \{rthakker, cgulino, daqingy, osalzman, ss5\} @andrew.cmu.edu}}%
%
\\        
Robotics Institute, Carnegie Mellon University$^{1}$
}

@@

%While, original sampling-based algorithms such as RRT~\cite{LK01} and PRM~\cite{KSLO96} only guaranteed to asymptotically return \emph{a} solution, if one exists, they did not provide any guarantees on the \emph{quality} of the solution, given some optimization criteria.
%Karaman and Frazzoli~\cite{KF11}, presented variants of PRM and RRT, named PRM* and RRT*, respectively that were shown to produce paths who's cost converges asymptotically to the minimal-cost path.
%Additional algorithms followed, increasing the converges rate by various techniques such as lazy dynamic programming~\cite{GSB15, JSCP15}, relaxing optimality to near-optimality~\cite{DB14, SH16} and more.
%
%However, recent years 
%Original planners such as RRT~\cite{LK01} and PRM~\cite{KSLO96} did not provide any guarantee on the \emph{s}

@@

\section{Motivating example---Minimal-Time Double Integrator}

We start by considering a simple yet important dynamical system---the double integrator. 
We are given a one-dimensional point robot with bounded velocity and bounded acceleration moving amid obstacles. We wish to compute the minimal-time trajectory between two states $x_s, x_g$.
A state in this model is described by 
the position $q \in \R$
and
the velocity $\dot{q}\in \R$ of the position
%each coordinate axis.
The dynamics of the system is described by:
$$
x = (q, \dot{q}); 
\hspace{5mm}
u = \ddot{q}.
$$
Here, the control $u \in [u_{\text{min}}, u_{\text{max}}]$ is the (bounded) acceleration.
